---
title: "HDP"
author: "Rnewbie"
date: "October 14, 2015"
output: html_document
---

Conformal Prediction using random forest at conconfidence level 0.80

```{r, cache = TRUE}
library(caret)
library(conformal)
library(randomForest)
showClass("ConformalClassification")
data <- readRDS("data.Rda")
in_train <- createDataPartition(data$Label, p = 0.8, list = FALSE)
train <- data[in_train, ]
test <- data[-in_train, ]
in_proper <- createDataPartition(train$Label, p = 0.7, list = FALSE)
proper <- train[in_proper, ]
cal <- train[-in_proper, ]
trControl <- trainControl(method = "cv", number = 5, savePredictions = TRUE)
set.seed(3)
### use test set only to save time
model <- train(Label~., data = cal, method = "rf",  trControl = trControl, predict.all = TRUE)

### confidence 0.80
example <- ConformalClassification$new()
example$CalculateCVScores(model = model)
example$CalculatePValues(new.data = test)
results_confidence_0.8 <- example$ClassPredictions$aggregate
results_prediction_0.8 <- as.data.frame(results_confidence_0.8)
actual <- test$Label
data_confidence_0.8 <- cbind(results_prediction_0.8, actual)
data_confidence_0.8 <- example$p.values$P
write.csv(data_confidence_0.8, file  = "data_confidence_0.8.csv", row.names = FALSE)

set.seed(333)
library(reshape2)
data <- read.csv("data_confidence_0.8.csv", header = TRUE)
data <- as.data.frame(data)
data <- cbind(sample = rownames(data), data)
data_significant <- example$p.values$Significance_p.values
ok <- apply(data_significant[, c("Bacteria", "Cancer", "Fungus", "Virus")], MARGIN = 1, FUN = sum)
ok <- as.data.frame(ok)
ok <- ok$ok
ok <- factor(ok, levels = c(0, 1, 2, 3, 4), labels = c("Zero", "One", "Two", "Three", "Four"))
data.m <- melt(data, id.vars = "sample")
data.m <- cbind(data.m, ok)
data.m$sample <- as.factor(data.m$sample)
data.m$ok <- as.factor(data.m$ok)
#levels(ok) <- ordered(ok, levels = c("0", "1", "2", "3", "4"))
#ok <- as.data.frame(ok)
### plot the stacked bar plot
#data <- data.m[, c("sample", "variable", "value", "ok")]
#data_2 <- data.frame(sample = factor(1), variable = "Null", value = 0, ok = "Zero")
#data <- rbind(data, data_2)
data <- data.m
data$ok <- as.factor(ok)
ggplot(data.m, aes(aes(factor(ok), valu))) + geom_boxplot(aes(weight = value, fill = variable), stat = "identity") +
  theme(
    #legend.position = ("none"),
    axis.text.y = element_text(color = "black", size = 20),
    axis.text.x = element_text(color = "black", size = 20),
    axis.title.y = element_text(color = "black", size = 30),
    axis.text.y = element_text(color = "black", size = 20)) + xlab(" ") + ylab("Count")



ggplot(data, aes(x = ok)) + geom_bar(aes(weight = value, fill = variable),
                                              position = 'fill') +
  theme(
    #legend.position = ("none"),
    axis.text.y = element_text(color = "black", size = 20),
    axis.ticks.length = unit(0.3, "cm"),
    axis.text.x = element_text(color = "black", size = 20),
    axis.title.y = element_text(color = "black", size = 30),
    axis.text.y = element_text(color = "black", size = 20)) + xlab(" ") + ylab("Count")



ggplot(data, aes(x = variable)) + geom_bar(aes(weight = value, fill = ok),
                                              position = 'fill') + geom_bar(aes(weight = value, fill = variable),
                                              position = 'fill') +
  theme(
    #legend.position = ("none"),
    axis.text.y = element_text(color = "black", size = 20),
    axis.ticks.length = unit(0.3, "cm"),
    axis.text.x = element_text(color = "black", size = 20),
    axis.title.y = element_text(color = "black", size = 30),
    axis.text.y = element_text(color = "black", size = 20)) + xlab(" ") + ylab("Count")




  


#plot the stacked bar plot
ggplot(df, aes(x = project)) + geom_bar(aes(weight=numbers, fill = component), position = 'fill') + scale_y_continuous("", breaks=NA) + scale_fill_manual(values = rev(brewer.pal(6, "Purples")))

#plot the stacked bar plot with polar coordinates
ggplot(df, aes(x = project)) + geom_bar(aes(weight=numbers, fill = component), position = 'fill') + scale_y_continuous("", breaks=NA) + scale_fill_manual(values = rev(brewer.pal(6, "Purples"))) + coord_polar()


ggplot(data.m, aes(x = sample, y = value, fill = variable)) +
  geom_bar(stat = "identity")






bacteria <- data$Bacteria
bacteria <- as.data.frame(bacteria)
cancer <- data$Cancer
cancer <- as.data.frame(cancer)
fungus <- data$Fungus
fungus <- as.data.frame(fungus)
virus <- data$Virus
virus <- as.data.frame(virus)
library(ggplot2)

ggplot() + geom_density(aes(x =bacteria), colour = "red", data = bacteria) +
  geom_density(aes(x = cancer), colour = "blue", data = cancer) +
  geom_density(aes(x = fungus), colour = "green", data = fungus) +
  geom_density(aes(x = virus), colour = "black", data = virus)





meltData <- melt(data_confidence_0.8)
meltData <- meltData[, c("Var2", "value")]
p <- ggplot(meltData, aes(x = Var2, y = value, fill = Var2)) + geom_boxplot() +
  theme(
    legend.position = ("none"),
    axis.text.y = element_text(color = "black", size = 20),
    axis.ticks.length = unit(0.3, "cm"),
    axis.text.x = element_text(color = "black", size = 20),
    axis.text.y = element_text(color = "black", size = 20)) + xlab("") + ylab("") 

data <- example$p.values$Significance_p.values
library(reshape2)
meltData <- melt(data)
meltData <- meltData[, c("Var2", "value")]

        
        
p + theme(legend.title = element_text(face = "italic", family = "Times", colour = "red", size = 14)) + 





### confidence 0.85
example_2 <- ConformalClassification$new()
example_2$initialize(confi = 0.85)
example_2 <- ConformalClassification$new()
example_2$CalculateCVScores(model = model)
example_2$CalculatePValues(new.data = test)
results_confidence_0.85 <- example_2$ClassPredictions$aggregate
results_prediction_0.85 <- as.data.frame(results_confidence_0.85)
actual <- test$Label
data_confidence_0.85 <- cbind(results_prediction_0.85, actual)
data_confidence_0.85 <- example_2$p.values$Significance_p.values

write.csv(data_confidence_0.85, file = "data_confidence_0.85.csv")
### confidence 0.90
example_3 <- ConformalClassification$new()
example_3$initialize(confi = 0.90)
example_3$CalculateCVScores(model = model)
example_3$CalculatePValues(new.data = test)
data_confidence_0.9 <- example_3$p.values$Significance_p.values)
write.csv(data_confidence_0.9, file = "data_confidence_0.9.csv")


example$initialize(0.90)
example$CalculatePValues(new.data = test)

data_1 <- read.csv("data_confidence_0.8.csv")
data_2 <- read.csv("data_confidence_0.85.csv")
data_3 <- read.csv("data_confidence_0.9.csv")

data_1$Level <- c("0.80")
data_2$Level <- c("0.85")
data_3$Level <- c("0.90")

data <- rbind(data_1, data_2, data_3)
data$Level <- as.factor(data$Level)

ggplot(data, aes(x = Bacteria, fill = Level)) + geom_bar()


data_confidence_0.8 <- as.factor(results_confidence_0.8)



p_values <- (example$p.values$P.values)



actual <- test$Label
conformal_prediction_results <- cbind(p_values, actual)
print(p_values)
significant <- example$p.values$Significance_p.values

```


```{r, cache = TRUE}
prediction_results <- as.data.frame(p_values)
actual <- test$Label
actual <- data.frame(actual)
conformal_prediction_results <- cbind(prediction_results, actual)
print(conformal_prediction_results)
```

Leave one class out validation



```{r, cache = TRUE}
library(caret)
library(conformal)
library(randomForest)
showClass("ConformalClassification")
data <- readRDS("data.Rda")
dat <- data
subs <- unique(dat$Label)
model_these <- vector(mode = "list", length = length(subs))
for(i in seq_along(subs))
  model_these[[i]] <- which(dat$Label != subs[i])
  names(model_these) <- paste0("Label", subs)
  LOCO <- train(x = data[, 1:20],
                y = dat[, 21],
                method = "J48",
                trControl = trainControl(method = "cv",
                                         index = model_these,
                                         classProbs = TRUE))
```





in_train <- createDataPartition(data$Label, p = 0.8, list = FALSE)
train <- data[in_train, ]
test <- data[-in_train, ]
in_proper <- createDataPartition(train$Label, p = 0.7, list = FALSE)
proper <- train[in_proper, ]
cal <- train[-in_proper, ]
trControl <- trainControl(method = "cv", number = 5, savePredictions = TRUE)
set.seed(3)
### use test set only to save time
model <- train(Label~., data = cal, method = "rf",  trControl = trControl, predict.all = TRUE)
